### 2025-01-27 paper/appendix.tex
annex

---
format:
  latex:
    template: bare.tex
---

## Appendix

Here's my awesome appendix.

>>>>

\section{Appendix}\label{appendix}

\subsection{Initial Grid Search}\label{initial-grid-search}

\subsubsection{Generator Params}\label{generator-params}

\paragraph{Linearly Separable}\label{linearly-separable}

\begin{longtable}{rrrrr}

\caption{\label{tbl-lin_sep-lambda_energy_exper}Results for Linearly
Separable data by energy penalty.}

\tabularnewline

  \toprule
  \textbf{Objective} & \textbf{Lambda Energy (exper)} & \textbf{Generator Type} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Objective} & \textbf{Lambda Energy (exper)} & \textbf{Generator Type} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0.01 & \textit{ECCo} & -9.91333e11 & 2.25464e12 \\
  full & 0.01 & \textit{Generic} & -5.71333e17 & 1.29951e18 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.01}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.54312}} & \color{blue}{\textbf{0.115996}} \\
  full & 0.01 & \textit{REVISE} & -15.6339 & 13.1813 \\
  vanilla & 0.01 & \textit{ECCo} & -4.28089 & 3.52021 \\
  vanilla & 0.01 & \textit{Generic} & -4.4476 & 3.47151 \\
  vanilla & 0.01 & \textit{Omniscient} & -5.11878 & 4.45562 \\
  vanilla & 0.01 & \textit{REVISE} & -4.91181 & 4.24403 \\
  full & 0.05 & \textit{ECCo} & -5.63008e5 & 1.28084e6 \\
  full & 0.05 & \textit{Generic} & -8.34667e17 & 1.89839e18 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.05}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.53131}} & \color{blue}{\textbf{0.114159}} \\
  full & 0.05 & \textit{REVISE} & -15.0237 & 12.5878 \\
  vanilla & 0.05 & \textit{ECCo} & -4.40037 & 3.6585 \\
  vanilla & 0.05 & \textit{Generic} & -4.38095 & 3.48267 \\
  vanilla & 0.05 & \textit{Omniscient} & -5.24923 & 4.6174 \\
  vanilla & 0.05 & \textit{REVISE} & -4.9445 & 4.21764 \\
  full & 0.1 & \textit{ECCo} & -674007.0 & 1.53289e6 \\
  full & 0.1 & \textit{Generic} & -1.71667e11 & 3.90456e11 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.1}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.56041}} & \color{blue}{\textbf{0.124295}} \\
  full & 0.1 & \textit{REVISE} & -15.6368 & 13.2452 \\
  vanilla & 0.1 & \textit{ECCo} & -4.28229 & 3.51532 \\
  vanilla & 0.1 & \textit{Generic} & -4.44665 & 3.47681 \\
  vanilla & 0.1 & \textit{Omniscient} & -5.11633 & 4.464 \\
  vanilla & 0.1 & \textit{REVISE} & -4.91309 & 4.25104 \\
  full & 0.5 & \textit{ECCo} & -11.7601 & 9.83205 \\
  full & 0.5 & \textit{Generic} & -1.064e18 & 2.41995e18 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.5}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.5405}} & \color{blue}{\textbf{0.122789}} \\
  full & 0.5 & \textit{REVISE} & -15.0277 & 12.5588 \\
  vanilla & 0.5 & \textit{ECCo} & -4.39923 & 3.65268 \\
  vanilla & 0.5 & \textit{Generic} & -4.38184 & 3.48393 \\
  vanilla & 0.5 & \textit{Omniscient} & -5.24831 & 4.61237 \\
  vanilla & 0.5 & \textit{REVISE} & -4.94731 & 4.2233 \\
  full & 1.0 & \textit{ECCo} & -11.5401 & 11.0622 \\
  full & 1.0 & \textit{Generic} & -1.70667e11 & 3.88205e11 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{1.0}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.58956}} & \color{blue}{\textbf{0.117255}} \\
  full & 1.0 & \textit{REVISE} & -15.7258 & 13.2676 \\
  vanilla & 1.0 & \textit{ECCo} & -4.27742 & 3.50817 \\
  vanilla & 1.0 & \textit{Generic} & -4.44409 & 3.4741 \\
  vanilla & 1.0 & \textit{Omniscient} & -5.11353 & 4.4628 \\
  vanilla & 1.0 & \textit{REVISE} & -4.91409 & 4.24885 \\
  full & 5.0 & \textit{ECCo} & -3.99166 & 3.12284 \\
  full & 5.0 & \textit{Generic} & -4.88333e17 & 1.11064e18 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{5.0}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.5325}} & \color{blue}{\textbf{0.117196}} \\
  full & 5.0 & \textit{REVISE} & -14.5887 & 12.1265 \\
  vanilla & 5.0 & \textit{ECCo} & -4.39614 & 3.64978 \\
  vanilla & 5.0 & \textit{Generic} & -4.37909 & 3.48341 \\
  vanilla & 5.0 & \textit{Omniscient} & -5.24668 & 4.60676 \\
  vanilla & 5.0 & \textit{REVISE} & -4.94655 & 4.22198 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{10.0}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-2.30721}} & \color{blue}{\textbf{0.73475}} \\
  full & 10.0 & \textit{Generic} & -1.69667e11 & 3.85893e11 \\
  full & 10.0 & \textit{Omniscient} & -2.53433 & 0.116736 \\
  full & 10.0 & \textit{REVISE} & -15.5346 & 13.0245 \\
  vanilla & 10.0 & \textit{ECCo} & -4.28116 & 3.50992 \\
  vanilla & 10.0 & \textit{Generic} & -4.4428 & 3.47049 \\
  vanilla & 10.0 & \textit{Omniscient} & -5.11933 & 4.46099 \\
  vanilla & 10.0 & \textit{REVISE} & -4.91285 & 4.24407 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{15.0}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-2.00576}} & \color{blue}{\textbf{0.48751}} \\
  full & 15.0 & \textit{Generic} & -4.91e17 & 1.11683e18 \\
  full & 15.0 & \textit{Omniscient} & -2.52833 & 0.11602 \\
  full & 15.0 & \textit{REVISE} & -14.3763 & 11.7494 \\
  vanilla & 15.0 & \textit{ECCo} & -4.3957 & 3.65194 \\
  vanilla & 15.0 & \textit{Generic} & -4.38497 & 3.48359 \\
  vanilla & 15.0 & \textit{Omniscient} & -5.24893 & 4.60484 \\
  vanilla & 15.0 & \textit{REVISE} & -4.94518 & 4.22746 \\\bottomrule

\end{longtable}

\paragraph{Moons}\label{moons}

\begin{longtable}{rrrrr}

\caption{\label{tbl-moons-lambda_energy_exper}Results for Moons data by
energy penalty.}

\tabularnewline

  \toprule
  \textbf{Objective} & \textbf{Lambda Energy (exper)} & \textbf{Generator Type} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Objective} & \textbf{Lambda Energy (exper)} & \textbf{Generator Type} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0.01 & \textit{ECCo} & -2.7995e22 & 6.38864e22 \\
  full & 0.01 & \textit{Generic} & -4.8906e30 & 1.11313e31 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.01}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-4.73844}} & \color{blue}{\textbf{5.0839}} \\
  full & 0.01 & \textit{REVISE} & -572.158 & 1245.03 \\
  vanilla & 0.01 & \textit{ECCo} & -15.5007 & 17.2501 \\
  vanilla & 0.01 & \textit{Generic} & -10.9068 & 11.8954 \\
  vanilla & 0.01 & \textit{Omniscient} & -12.6633 & 14.3968 \\
  vanilla & 0.01 & \textit{REVISE} & -11.2239 & 13.0133 \\
  full & 0.05 & \textit{ECCo} & -1.54854e16 & 3.52394e16 \\
  full & 0.05 & \textit{Generic} & -2.21669e20 & 5.00175e20 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.05}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-4.41}} & \color{blue}{\textbf{4.48466}} \\
  full & 0.05 & \textit{REVISE} & -1036.78 & 2300.0 \\
  vanilla & 0.05 & \textit{ECCo} & -15.4978 & 17.2215 \\
  vanilla & 0.05 & \textit{Generic} & -11.697 & 12.8139 \\
  vanilla & 0.05 & \textit{Omniscient} & -12.4116 & 14.1033 \\
  vanilla & 0.05 & \textit{REVISE} & -11.3225 & 13.1404 \\
  full & 0.1 & \textit{ECCo} & -3408.28 & 7734.83 \\
  full & 0.1 & \textit{Generic} & -5.21659e30 & 1.18648e31 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.1}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-4.78488}} & \color{blue}{\textbf{5.1212}} \\
  full & 0.1 & \textit{REVISE} & -287.874 & 593.988 \\
  vanilla & 0.1 & \textit{ECCo} & -15.4788 & 17.2353 \\
  vanilla & 0.1 & \textit{Generic} & -10.9226 & 11.9247 \\
  vanilla & 0.1 & \textit{Omniscient} & -12.666 & 14.3869 \\
  vanilla & 0.1 & \textit{REVISE} & -11.2936 & 13.1035 \\
  full & 0.5 & \textit{ECCo} & -7.08577 & 7.51393 \\
  full & 0.5 & \textit{Generic} & -1.1064e31 & 2.53239e31 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.5}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-4.58057}} & \color{blue}{\textbf{4.8256}} \\
  full & 0.5 & \textit{REVISE} & -1187.61 & 2643.72 \\
  vanilla & 0.5 & \textit{ECCo} & -15.4966 & 17.1932 \\
  vanilla & 0.5 & \textit{Generic} & -11.7071 & 12.8003 \\
  vanilla & 0.5 & \textit{Omniscient} & -12.3897 & 14.1104 \\
  vanilla & 0.5 & \textit{REVISE} & -11.2965 & 13.1122 \\
  full & 1.0 & \textit{ECCo} & -6.06278 & 6.32519 \\
  full & 1.0 & \textit{Generic} & -1.57758e33 & 3.59342e33 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{1.0}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-4.66436}} & \color{blue}{\textbf{4.88547}} \\
  full & 1.0 & \textit{REVISE} & -1157.26 & 2585.3 \\
  vanilla & 1.0 & \textit{ECCo} & -15.4915 & 17.2592 \\
  vanilla & 1.0 & \textit{Generic} & -10.8969 & 11.888 \\
  vanilla & 1.0 & \textit{Omniscient} & -12.6685 & 14.4499 \\
  vanilla & 1.0 & \textit{REVISE} & -11.2874 & 13.1369 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{5.0}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-2.56504}} & \color{blue}{\textbf{2.06543}} \\
  full & 5.0 & \textit{Generic} & -1.16971e28 & 2.66145e28 \\
  full & 5.0 & \textit{Omniscient} & -4.28955 & 4.30748 \\
  full & 5.0 & \textit{REVISE} & -530.204 & 1163.55 \\
  vanilla & 5.0 & \textit{ECCo} & -15.4763 & 17.1877 \\
  vanilla & 5.0 & \textit{Generic} & -11.6655 & 12.7364 \\
  vanilla & 5.0 & \textit{Omniscient} & -12.3937 & 14.1141 \\
  vanilla & 5.0 & \textit{REVISE} & -11.2976 & 13.0533 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{10.0}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.76439}} & \color{blue}{\textbf{0.973615}} \\
  full & 10.0 & \textit{Generic} & -1.54318e33 & 3.51163e33 \\
  full & 10.0 & \textit{Omniscient} & -4.44467 & 4.56008 \\
  full & 10.0 & \textit{REVISE} & -1515.03 & 3402.96 \\
  vanilla & 10.0 & \textit{ECCo} & -15.5074 & 17.275 \\
  vanilla & 10.0 & \textit{Generic} & -10.9077 & 11.8867 \\
  vanilla & 10.0 & \textit{Omniscient} & -12.6771 & 14.4225 \\
  vanilla & 10.0 & \textit{REVISE} & -11.2735 & 13.1031 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{15.0}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.36625}} & \color{blue}{\textbf{0.3652}} \\
  full & 15.0 & \textit{Generic} & -5.32108e28 & 1.21152e29 \\
  full & 15.0 & \textit{Omniscient} & -4.34376 & 4.38045 \\
  full & 15.0 & \textit{REVISE} & -473.027 & 1034.8 \\
  vanilla & 15.0 & \textit{ECCo} & -15.4703 & 17.1898 \\
  vanilla & 15.0 & \textit{Generic} & -11.6941 & 12.7669 \\
  vanilla & 15.0 & \textit{Omniscient} & -12.3895 & 14.0956 \\
  vanilla & 15.0 & \textit{REVISE} & -11.2868 & 13.0587 \\\bottomrule

\end{longtable}

\paragraph{Circles}\label{circles}

\begin{longtable}{rrrrr}

\caption{\label{tbl-circles-lambda_energy_exper}Results for Circles data
by energy penalty.}

\tabularnewline

  \toprule
  \textbf{Objective} & \textbf{Lambda Energy (exper)} & \textbf{Generator Type} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Objective} & \textbf{Lambda Energy (exper)} & \textbf{Generator Type} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \endfoot
  \endlastfoot
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.01}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.26251}} & \color{blue}{\textbf{0.422879}} \\
  full & 0.01 & \textit{Generic} & -1.49019 & 0.710317 \\
  full & 0.01 & \textit{Omniscient} & -5.20834 & 5.24965 \\
  full & 0.01 & \textit{REVISE} & -2.71465e26 & 6.36795e26 \\
  vanilla & 0.01 & \textit{ECCo} & -9.32869 & 7.33883 \\
  vanilla & 0.01 & \textit{Generic} & -8.88908 & 6.88126 \\
  vanilla & 0.01 & \textit{Omniscient} & -8.67329 & 6.86953 \\
  vanilla & 0.01 & \textit{REVISE} & -8.65247 & 6.79692 \\
  full & 0.05 & \textit{ECCo} & -1.2868 & 0.396551 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.05}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-1.20911}} & \color{blue}{\textbf{0.356273}} \\
  full & 0.05 & \textit{Omniscient} & -5.0777 & 5.09456 \\
  full & 0.05 & \textit{REVISE} & -5.91165e27 & 1.36148e28 \\
  vanilla & 0.05 & \textit{ECCo} & -9.35176 & 7.31732 \\
  vanilla & 0.05 & \textit{Generic} & -8.854 & 6.87298 \\
  vanilla & 0.05 & \textit{Omniscient} & -8.70242 & 6.95789 \\
  vanilla & 0.05 & \textit{REVISE} & -8.52208 & 6.75727 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.1}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.2021}} & \color{blue}{\textbf{0.382734}} \\
  full & 0.1 & \textit{Generic} & -1.50229 & 0.735365 \\
  full & 0.1 & \textit{Omniscient} & -5.17466 & 5.22628 \\
  full & 0.1 & \textit{REVISE} & -3.0594e26 & 7.70324e26 \\
  vanilla & 0.1 & \textit{ECCo} & -9.32978 & 7.32099 \\
  vanilla & 0.1 & \textit{Generic} & -8.88085 & 6.86308 \\
  vanilla & 0.1 & \textit{Omniscient} & -8.68505 & 6.90258 \\
  vanilla & 0.1 & \textit{REVISE} & -8.67959 & 6.80887 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.5}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.12388}} & \color{blue}{\textbf{0.216889}} \\
  full & 0.5 & \textit{Generic} & -1.20782 & 0.352005 \\
  full & 0.5 & \textit{Omniscient} & -5.09228 & 5.1182 \\
  full & 0.5 & \textit{REVISE} & -5.97244e27 & 1.36572e28 \\
  vanilla & 0.5 & \textit{ECCo} & -9.35338 & 7.30155 \\
  vanilla & 0.5 & \textit{Generic} & -8.89415 & 6.91671 \\
  vanilla & 0.5 & \textit{Omniscient} & -8.67963 & 6.9307 \\
  vanilla & 0.5 & \textit{REVISE} & -8.52507 & 6.74796 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{1.0}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.099}} & \color{blue}{\textbf{0.163365}} \\
  full & 1.0 & \textit{Generic} & -1.49485 & 0.726287 \\
  full & 1.0 & \textit{Omniscient} & -5.15975 & 5.20449 \\
  full & 1.0 & \textit{REVISE} & -3.09069e26 & 7.22344e26 \\
  vanilla & 1.0 & \textit{ECCo} & -9.33801 & 7.36386 \\
  vanilla & 1.0 & \textit{Generic} & -8.8619 & 6.85196 \\
  vanilla & 1.0 & \textit{Omniscient} & -8.69785 & 6.89941 \\
  vanilla & 1.0 & \textit{REVISE} & -8.69498 & 6.85371 \\
  full & 5.0 & \textit{ECCo} & -1.75204 & 0.154399 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{5.0}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-1.21285}} & \color{blue}{\textbf{0.362686}} \\
  full & 5.0 & \textit{Omniscient} & -5.13516 & 5.16338 \\
  full & 5.0 & \textit{REVISE} & -1.09598e28 & 2.50339e28 \\
  vanilla & 5.0 & \textit{ECCo} & -9.36397 & 7.32382 \\
  vanilla & 5.0 & \textit{Generic} & -8.88498 & 6.90503 \\
  vanilla & 5.0 & \textit{Omniscient} & -8.70333 & 6.9289 \\
  vanilla & 5.0 & \textit{REVISE} & -8.51631 & 6.72565 \\
  full & 10.0 & \textit{ECCo} & -1.01708e6 & 2.31516e6 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{10.0}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-1.48827}} & \color{blue}{\textbf{0.701741}} \\
  full & 10.0 & \textit{Omniscient} & -5.13432 & 5.15897 \\
  full & 10.0 & \textit{REVISE} & -3.74376e26 & 9.08858e26 \\
  vanilla & 10.0 & \textit{ECCo} & -9.31463 & 7.32684 \\
  vanilla & 10.0 & \textit{Generic} & -8.87348 & 6.86388 \\
  vanilla & 10.0 & \textit{Omniscient} & -8.7046 & 6.89274 \\
  vanilla & 10.0 & \textit{REVISE} & -8.68653 & 6.83497 \\
  full & 15.0 & \textit{ECCo} & -3.31332e13 & 7.53714e13 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{15.0}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-1.21817}} & \color{blue}{\textbf{0.370377}} \\
  full & 15.0 & \textit{Omniscient} & -5.19548 & 5.23317 \\
  full & 15.0 & \textit{REVISE} & -9.01467e27 & 2.0592e28 \\
  vanilla & 15.0 & \textit{ECCo} & -9.37662 & 7.34277 \\
  vanilla & 15.0 & \textit{Generic} & -8.86149 & 6.8695 \\
  vanilla & 15.0 & \textit{Omniscient} & -8.69488 & 6.95691 \\
  vanilla & 15.0 & \textit{REVISE} & -8.50583 & 6.72685 \\\bottomrule

\end{longtable}
